Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-07-12 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
updated graphics, changes to acknowledgement, updated numerical section to remove third-order-if-linear-fwd claim and integrated continuation remark into 3d example

%
\begin{proposition}
\label{thm:error_estimate_dual}
Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let the variational form
%
\begin{equation}
\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:supadjsys_prop}
\end{equation}
%
represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define an adjoint problem
%
\begin{equation}
\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:superAdjEq}
\end{equation}
for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys_prop}, and where
%Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
%
%\begin{equation}
%\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
%\end{equation}
%
where $\mathcal{Q}:(U_{HF} \times U_{HF} \times Q_{HF})^2 \to \R$ is a linear functional defined by,
%
\begin{equation}
\mathcal{Q}(\Phi)=\mathcal{M}'_{HF}(\Psi_{LF})(\Phi).
\label{eq:supadjout}
\end{equation}
%
Then we have,
%
\begin{multline}
\label{eq:finErrExp}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}) + \mathcal{R}_{\mathscr{R}} + \mathcal{R}
\end{multline}
%
where $\mathcal{R}_{\mathscr{R}}$ is a second-order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $\mathcal{R}$ is as defined in \Cref{thm:error_estimate}. %\red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
%
\end{proposition}
%
\begin{proof}
%
The proof simply follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
%
\begin{equation}
\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:supadjsys}
\end{equation}
%
which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the adjoint problem
%
\begin{equation}
\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:superAdjEq}
\end{equation}
%
for the supplementary adjoint $\Lambda$. The error in the linear output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
%
\begin{equation}
\label{eq:adjOutErr}
\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF})(\Lambda) + R_{\mathscr{R}},
\end{equation}
%
where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$ in \Cref{eq:superAdjEq}. This implies the required result. %\red{What is the classical notation for adjoint problems? Is it okay that we're breaking from the previous notation where a second pair of parentheses denotes things that we are linear in?}
%
\end{proof}
%
We note that if the state equations of the high-fidelity model are linear, the remainder term $R_\mathscr{R}$ in the supplementary adjoint formulation in \Cref{eq:adjOutErr} vanishes, and the error estimate in \Cref{eq:finErrExp} becomes fully third-order. This occurs even if the QoI functional $I$ is nonlinear.
%If the state equations of the high fidelity model are linear, the derivative of the Lagrangian in~\Cref{eq:InvsOpt_auglag} is linear. In this case, the $R_{\mathscr{R}}$ term in~\Cref{eq:finErrExp} disappears, even if the QoI functional $I$ is nonlinear, and we get a fully third order error estimate.

>>>>

%
\begin{proposition}
\label{thm:error_estimate_dual}
Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let the variational form
%
\begin{equation}
\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:supadjsys_prop}
\end{equation}
%
represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define an adjoint problem
%
\begin{equation}
\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:superAdjEq}
\end{equation}
for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys_prop}, and where
%Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
%
%\begin{equation}
%\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
%\end{equation}
%
where $\mathcal{Q}:(U_{HF} \times U_{HF} \times Q_{HF})^2 \to \R$ is a linear functional defined by,
%
\begin{equation}
\mathcal{Q}(\Phi)=\mathcal{M}'_{HF}(\Psi_{LF})(\Phi).
\label{eq:supadjout}
\end{equation}
%
Then we have,
%
\begin{multline}
\label{eq:finErrExp}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}) + \mathcal{R}_{\mathscr{R}} + \mathcal{R}
\end{multline}
%
where $\mathcal{R}_{\mathscr{R}}$ is a second-order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $\mathcal{R}$ is as defined in \Cref{thm:error_estimate}. %\red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
%
\end{proposition}
%
\begin{proof}
%
The proof simply follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
%
\begin{equation}
\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:supadjsys}
\end{equation}
%
which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the adjoint problem
%
\begin{equation}
\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:superAdjEq}
\end{equation}
%
for the supplementary adjoint $\Lambda$. The error in the linear output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
%
\begin{equation}
\label{eq:adjOutErr}
\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF})(\Lambda) + R_{\mathscr{R}},
\end{equation}
%
where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$ in \Cref{eq:superAdjEq}. This implies the required result. %\red{What is the classical notation for adjoint problems? Is it okay that we're breaking from the previous notation where a second pair of parentheses denotes things that we are linear in?}
%
\end{proof}
%
%We note that if the state equations of the high-fidelity model are linear, the remainder term $R_\mathscr{R}$ in the supplementary adjoint formulation in \Cref{eq:adjOutErr} vanishes, and the error estimate in \Cref{eq:finErrExp} becomes fully third-order. This occurs even if the QoI functional $I$ is nonlinear.
%If the state equations of the high fidelity model are linear, the derivative of the Lagrangian in~\Cref{eq:InvsOpt_auglag} is linear. In this case, the $R_{\mathscr{R}}$ term in~\Cref{eq:finErrExp} disappears, even if the QoI functional $I$ is nonlinear, and we get a fully third order error estimate.

### 2017-07-12 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
updated graphics, changes to acknowledgement, updated numerical section to remove third-order-if-linear-fwd claim and integrated continuation remark into 3d example

The QoI region is $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The parameters $q$ we wish to infer correspond to the forcing function. The observations are sparse measurements of the state.
\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). We arbitarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
  \label{subfig:obsMF1}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
  \label{subfig:obsMF1_2}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in H^1(\Omega),
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U_{LF}
\end{equation}
differs from the high-fidelity model only in that $U_{LF}$ is limited to the space of constant functions over $\Omega$; we maintain $f(q)=q$. The intermediate mixed-fidelity models thus have parameter fields (and forcing functions) that are constant over the subregions of the domain where the low-fidelity model is used; disconnected low-fidelity regions still share the same parameter value. The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. Also for ease of implementation and for localizing the error, the forcing field and its auxiliary and supplementary adjoint conterparts are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions using a penalty term. Although the chosen pair of models has the potential to give mixed-fidelity models with fewer degreees of freedom in the parameter, this is not the case in our implementation; however, we are not looking to demonstrate computational savings with this example, but rather to explore the behavior of \Cref{alg:refSeries} when applied to such a pair of models. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
%\subfloat[MF$_1$ ($10\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF1}
%} \\
%\subfloat[MF$_3$ ($30\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF3}
%} \\
%\subfloat[MF$_6$ ($60\%$ HF)]{
%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
%  \label{subfig:svfparamMF6}
%} \\
%\subfloat[HF]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
%	\label{subfig:svfparamHF}
%}
%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare 
%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
the bottom two figures of \Cref{fig:svfRefParams}
). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see 
%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
the top two figures of \Cref{fig:svfRefParams}
) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

@@

\Cref{tab:ref3D_diffmesh} shows the error at the end of each adaptive iteration. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem. The high-fidelity inverse problem does not converge when the low-fidelity solution is used as an initial guess. Instead, we solve the inverse problem for an intermediate model
%
\begin{equation}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q)
\end{equation}
%
with $k_r=0$, and use the solution as an initial guess for the high-fidelity problem; this is equivalent to using two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
%
\begin{table}[htbp]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\
& & & & (Estimated) & (Actual) & Error (Actual)  \\ \hline
LF   & 0    & 9537  & 168710 & -16463 & -85663 & -103    \\
MF01 & 5.2  & 13417 & 167366 & -7207  & -84319 & -102    \\
MF02 & 11.4 & 17895 & 89777  & -6208  & -6730  & -8.10   \\
MF03 & 16.3 & 21001 & 85880  & -2473  & -2833  & -3.41   \\
MF04 & 22.0 & 24528 & 83902  & -711   & -855   & -1.03   \\
MF05 & 27.7 & 27984 & 83119  & 32     & -72    & -0.087  \\
HF   & 100  & 70785 & 83047  & --     & --     & --    \\ \hline
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
\label{tab:ref3D_diffmesh}
\end{table}
%

>>>>

The QoI region is $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The parameters $q$ we wish to infer correspond to the forcing function. The observations are sparse measurements of the state.
\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). We arbitrarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_qoi/yarp.pdf}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp0.pdf}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp1.pdf}
  \label{subfig:obsMF1}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_qoi/yarp2.pdf}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_data/yarp.pdf}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \includegraphics[width=0.162\textwidth]{vs_data/yarp0.pdf}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
  \includegraphics[width=0.171\textwidth]{vs_data/yarp1.pdf}
  \label{subfig:obsMF1_2}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_data/yarp2.pdf}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in H^1(\Omega),
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U_{LF}
\end{equation}
differs from the high-fidelity model only in that $U_{LF}$ is limited to the space of constant functions over $\Omega$; we maintain $f(q)=q$. The intermediate mixed-fidelity models thus have parameter fields (and forcing functions) that are constant over the subregions of the domain where the low-fidelity model is used; disconnected low-fidelity regions still share the same parameter value. The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. Also for ease of implementation and for localizing the error, the forcing field and its auxiliary and supplementary adjoint counterparts are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions using a penalty term. Although the chosen pair of models has the potential to give mixed-fidelity models with fewer degrees of freedom in the parameter, this is not the case in our implementation; however, we are not looking to demonstrate computational savings with this example, but rather to explore the behavior of \Cref{alg:refSeries} when applied to such a pair of models. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
%\subfloat[MF$_1$ ($10\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF1}
%} \\
%\subfloat[MF$_3$ ($30\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF3}
%} \\
%\subfloat[MF$_6$ ($60\%$ HF)]{
%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
%  \label{subfig:svfparamMF6}
%} \\
%\subfloat[HF]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
%	\label{subfig:svfparamHF}
%}
%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare 
%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
the bottom two figures of \Cref{fig:svfRefParams}). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see 
%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

@@

\Cref{tab:ref3D_diffmesh} shows the error at the end of each adaptive iteration. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem. We note that convergence of the high-fidelity inverse problem is sensitive to the initial guess; the solve does not converge when the low-fidelity solution is used as an initial guess. Instead, we solve the inverse problem for an intermediate model
%
\begin{equation}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q)
\end{equation}
%
with $k_r=0$, and use the solution as an initial guess for the high-fidelity problem; this is equivalent to using two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$. In comparison, the adaptive algorithm needs no such continuation in $k_r$ to converge; each step can be viewed as implicit continuation in the addition of high-fidelity regions.
%
\begin{table}[htbp]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\
& & & & (Estimated) & (Actual) & Error (Actual)  \\ \hline
LF   & 0    & 9537  & 168710 & -16463 & -85663 & -103    \\
MF01 & 5.2  & 13417 & 167366 & -7207  & -84319 & -102    \\
MF02 & 11.4 & 17895 & 89777  & -6208  & -6730  & -8.10   \\
MF03 & 16.3 & 21001 & 85880  & -2473  & -2833  & -3.41   \\
MF04 & 22.0 & 24528 & 83902  & -711   & -855   & -1.03   \\
MF05 & 27.7 & 27984 & 83119  & 32     & -72    & -0.087  \\
HF   & 100  & 70785 & 83047  & --     & --     & --    \\ \hline
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
\label{tab:ref3D_diffmesh}
\end{table}
%
